---
title       : United States Storms Data Summary
subtitle    : Developing Data Products Course Project
author      : Rajiv Shrestha
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: libraries/nvd3}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## US Storms and Its impact

  - This project briefly presents into the storm and weather data of United States
  - The project allows user to look into specific data 
  - The project allows user to look into specific year of data
  - This provides user with the visual representation of the data in form of charts.

--- .class#id

## Between 1950 and 2011 severe weather events caused at least
```{r, echo=FALSE}
library(data.table)
library(rCharts)
library(reshape2)
library(knitr)

dt <- fread('./../shiny-app/data/events.agg.csv')
dt.agg.year <- dt[, list(Count=sum(COUNT), Injuries=sum(INJURIES), Fatalities=sum(FATALITIES)), by=list(YEAR)]
```

 - `r format(sum(dt$FATALITIES), big.mark=' ')` deaths
 - `r format(sum(dt$INJURIES), big.mark=' ')` injuries
 - $`r format(round((sum(dt$PROPDMG) + sum(dt$CROPDMG)) / 1000), big.mark=' ')` billion worth of damage
 

---

## Events chart
```{r nvd3plot2, results = 'asis', comment = NA, message = F, echo = F} 
data <- melt(dt.agg.year[, list(YEAR=YEAR, Injuries=Injuries, Fatalities=Fatalities)], id='YEAR')
populationImpact <- nPlot(
    value ~ YEAR, group = 'variable', data = data[order(-YEAR, variable, decreasing = T)],
    type = 'stackedAreaChart', dom = 'populationImpact'
)
        
populationImpact$chart(margin = list(left = 100))
populationImpact$yAxis( axisLabel = "Affected", width = 80)
populationImpact$xAxis( axisLabel = "Year", width = 70)
        
populationImpact
    
```

---

## More information and content

- Demo of the project is available in shinyapps location
[ShinyApps Demo](https://rajivd.shinyapps.io/assignment/)
- Github project is available here [Github link](https://github.com/RajivShrestha/DevelopingDataProducts-Shiny)
- To learn more and become expert: enroll [Coursera Data Science Specialization program](https://www.coursera.org/specializations/jhu-data-science/1)
